A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-17 paper.tex
Added some comments

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
We will now explain how to define the BV bracket.  First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{dR} F & : & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{dR} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{dR} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{dR}F$:
\[
X_F := \omega \circ \d_{dR} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.  Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.  The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
\end{proof}

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
\begin{prop}
Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
&\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
&\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
\end{align*}
and
\begin{align*}
I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
&\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
&\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
\end{align*}
where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
\end{prop}
%
%The matter sector of the theory is labeled by the BRST fields:
%\begin{itemize}
%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
%\end{itemize} 
%which together define the (abelian) local Lie algebra
%\[
%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
%\]

>>>>

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
We will now explain how to define the BV bracket.  First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
\[
X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.  Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.  The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.

I'll try to write this as Pavel did in 8d, so write as a proposition the action of $Q_{\mr{hol}} + tQ'$, and observe that it induces this deformation.}
\end{proof}

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
\begin{prop}
Consider a square-zero supercharge $Q = Q_+ \otimes w_+ + Q_- \otimes w_-$.  After reduction to $\mr O(4)$, the interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}(Q) &= \int (\Gamma(Q_+, \lambda_-)(w_+,u_-), A^*) + (\Gamma(Q_-, \lambda_+)(w_-,u_+), A^*) + \langle Q_+, \lambda_+ \rangle (w_+ \wedge u_+, \phi^*) + \langle Q_-, \lambda_- \rangle (\omega(w_- \wedge u_-), \phi^*) + \\
&\quad + \frac12 \bigg( \langle \rho(F_A)Q_+, \lambda_+^*\rangle(w_+,u_+^*) + \langle \rho(F_A)Q_-, \lambda_-^*\rangle(w_-,u_-^*) +\\
&\qquad \qquad \qquad \qquad \langle\rho(\d_A (w_+ \wedge u_-^*,\phi))Q_+, \lambda_-^*\rangle + \langle\rho(\d_A (\omega(w_- \wedge u_+^*)),\phi)Q_-, \lambda_+^*\rangle \bigg),
\end{align*}
and
\begin{align*}
I^{(2)}(Q_1, Q_2) &= \int \frac 12 \left( g(\Gamma(Q_+, Q_-), \Gamma(\lambda^*_+, \lambda^*_-)) (w_+, w_-) (u_+^*,u_-^*) \right) + \\
&\quad - \frac 12 \big( \langle Q_+,\lambda_+^*\rangle^2(w_+,u_+^*)^2 + \langle Q_-,\lambda_-^*\rangle^2(w_-,u_-^*)^2 \big) - \langle Q_+,\lambda_+^*\rangle \langle Q_-, \lambda_-^*\rangle (w_+,u_+^*)(w_-,u_-^*) +\\
&\quad - (\langle Q_+, Q_+ \rangle (\omega^{-1}(w_+ \wedge w_+),\phi) + \langle Q_-, Q_- \rangle (w_- \wedge w_-,\phi)  ) c^*,
\end{align*}
where $\omega$ indicates the canonical isomorphism $\omega \colon \wedge^2(W^*) \to \wedge^2(W)$ (the Killing form for $\so(W^*)$).
\end{prop}

\chris{todo: $(1,0)$, $(2,0)$, $(1,1)$ as above, with $U = T^*\gg$.  Then $(2,1)$ and generic $(2,2)$ arise as deformations of $(1,1)$ by dimensional reduction from 5d.  Finally the special $(2,2)$ arises by dimensional reduction from the 5d B-twist.}
